---
title: "Basic Usage"
output: 
  html_document: 
    toc: true
    toc_float: true
    theme: yeti
    highlight: textmate
vignette: >
  %\VignetteIndexEntry{[basicusage]}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```
# Setup
Library the package and a solver (glpk)
```{r setup, warning = FALSE}
library(dfsOptimizer)
```


## Building Optimizer and getting lineups
Example of instantiating an Optimizer object, adding players from an internal dataset (`nhl_players`),
generating 5 lineups.

```{r}
# Instantiate
mod <- create_optimizer(site = 'DRAFTKINGS', sport = 'HOCKEY', contest_type = 'CLASSIC')
# Add players
mod <- add_players_from_df(mod, nhl_players)
# Generate lineups
lineups <- build_lineups(mod, num_lineups = 5, verbose = FALSE)
```

## View the lineups
You can view the lineups simply by calling the object saved by `build_lineups`.

```{r}
lineups
```

You can access the individual lineups with standard '[' indexing
```{r}
lineups[1]
lineups[[2]]
```

Finally, you may to extract the lineups to a list, 
To do so, you can simply run `as.list(lineups)`
```{r}
# Here we're getting the total fpts from every lineup using sapply
colSums(sapply(as.list(lineups), '[[', 'fpts'))
```

## Lineup Summary
Lineup summary provides information about how often individual players were selected for lineups (count and percentage),
which teams were selected most often, and a measure of lineup variance (higher Jaccard Distance means more variance across lineups)
```{r}
# Summary stats
summary(lineups)

```

## Export the lineups
The format of the file output by export_lineups is determined by the Site, Sport, and Contest Type.
```{r eval=FALSE}
export_lineups(lineups, file = 'lineup_export.csv')
```

