---
title: "Experimentation and Back-Testing"
output: 
  html_document: 
    toc: true
    toc_float: true
    theme: yeti
    highlight: textmate
vignette: >
  %\VignetteIndexEntry{rules}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  eval = FALSE,
  comment = "#>"
)
```

```{r echo = FALSE}
library(dfsOptimizer)
```

When you're using a tool like `dfsOptimizer`, it can be helpful to do real-world experiments to fine-tune the methods and constraints
you choose to apply when you're building lineups.  For instance, should you stack players?  Should you limit the max salary?

To make this easier, you can use the `compare_lineups_with_actuals` function.

## Compare lineups with actual performance

Given a set up lineups generated using `build_lineups`, the `compare_lineups_with_actuals` can quickly calculate the
real-world value of those lineups, given a data.frame containing actual scores.

An example: You joined a contest on a DFS site, and you didn't win -- you want to see whether you would have performed better
in that contest had you done something differently with your lineup construction.

So, you go get the players' *actual* fantasy points for that contest, and using `compare_lineups_with_actuals`, can start testing.

In the following example, `actuals` is a data.frame with three columns: 
- `id`: The player's ID
- `fullname`: The player's fullname
- `actuals`: The actual fantasy points for that player

```{r}
# 
```

