---
title: "Customizating your Optimizer"
output: 
  html_document: 
    toc: true
    toc_float: true
    theme: yeti
    highlight: textmate
vignette: >
  %\VignetteIndexEntry{rules}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  eval = FALSE,
  comment = "#>"
)
```

```{r echo = FALSE}
library(dfsOptimizer)
```

The package comes with basic functions to specify constraints within your 
optimizer model, in order to better tune your lineups.

# Block Players
If you'd like to omit specific players, you can do so by ID.
```{r}

```

# Lock Players
If you want to ensure that specific players are included in all lineups.
```{r}

```

# Same Team Stacking
There are multiple ways to stack teams together.

## Example 1

## Example 2

# Restrict Opposing Positions
Useful in cases where you want to ensure opposing positions from two teams aren't included 
in the lineup, like preventing one team's QB and the other team's DST.

Here's an example that prevents the lineups from including one team's goalie
and _any forward or defenseman_ on the opposing team.
```{r}

```

# Force Opposing Positions
When you want to ensure that two positions from opposite teams are included. For 
example, if you want to ensure that the lineups included at least one pair of 
Team A's QB and Team B's WR.

```{r}

```

# Player Exposures

## Maximium Exposure
```{r}

```

## Minimum Exposure
```{r}

```

## Global Exposures 

Sometimes you want to set global exposures, so that no single player is selected
for a lineup more than X% of the time.  You can use the global maximum exposure for that.

**NOTE:** Individual player exposures supersede the global exposures. So, if you set
Sidney Crosby's Max-Exposure to .8, and the global max to .5, Sidney Crosby 
may end up in 80% of your lineups, while no other player will be greater than 50%.

```{r}

```

# Specific Positions for FLEX/UTIL positions

This has no effect on lineups where no FLEX/UTIL positions are included.

```{r}

```

# Maximium Repeating Players

Set the maximum number of players allowed to repeat across lineups.

```{r}

```

# Set a minimum budget

```{r}

```

# Set Multiplier Position
This applies to Draftking's Captain Mode and Fanduel's MVP mode, where one player
is designated a multiplier position, where their salary and pts are doubled.

Sometimes, you may want to limit the set of players who are eligible for this
position (e.g., you definitely want either a QB or a WR, not DST or TE)

```{r}

```

# Variance

## Global Variance

## Player Level Variance