---
title: "Customizating your Optimizer"
output: 
  html_document: 
    toc: true
    toc_float: true
    theme: yeti
    highlight: textmate
vignette: >
  %\VignetteIndexEntry{rules}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  eval = FALSE,
  comment = "#>"
)
```

```{r echo = FALSE}
library(dfsOptimizer)
```

The package comes with basic functions to specify constraints within your 
optimizer model, in order to better tune your lineups.

# Blocking and Locking Players
First step here is to get player IDs. Using an optimizer object, you can
get individual player IDs by name like so:
```{r}
# Opt is an optimizer object
single_player_id <- get_player_id(opt, name = 'Sidney Crosby')
```

Or, you can use `get_player_data`, which will return a data.frame of player
data, where you can filter by name to get IDs
```{r}
player_data <- get_player_data(opt)
multiple_player_ids <- player_data[fullname %in% c('Carey Price', 'Sidney Crosby')]$id
```

## Block Players
If you'd like to omit specific players, you can block by ID.
```{r}
# Single Player
opt <- block_players_by_id(opt, player_ids = single_player_id)

# Multiple players use the same syntax
opt <- block_players_by_id(opt, player_ids = multiple_player_ids)
```

## Lock Players
If you want to ensure that specific players are included in all lineups.
```{r}
# As with blocking, player_ids can be a scalar or vector of IDs
opt <- lock_players_by_id(opt, player_ids = pids)
```

# Same Team Stacking
Useful in cases where you want to stack players from the same team together. For
instance, you may want to stack a QB and a WR together.

```{r}
# Stacking QB and WR from the same team together
opt <- opt %>%
  add_team_stack(positions = c('QB', 'WR'))
```
You can specify the number of stacks - so if you want TWO separate QB/WR stacks,
you can use:
```{r}
# Stacking QB and WR from the same team together
opt <- opt %>%
  add_team_stack(positions = c('QB', 'WR'), nstacks = 2)
```

At times, you may wish to have an additional optional position; say, you want
to stack a QB/WR pair and *one additional player of either* TE, RB, or WR:
```{r}
# Stacking QB and WR from the same team together
opt <- opt %>%
  add_team_stack(positions = c('QB', 'WR'), opt_positions = c('TE','WR','RB'))
```

# Restrict Opposing Positions
Useful in cases where you want to ensure opposing positions from two teams aren't included 
in the lineup, like preventing one team's QB and the other team's DST.

Here's an example that prevents the lineups from including one team's goalie
and _any forward or defenseman_ on the opposing team.
```{r}
opt <- opt %>% 
  restrict_opposing_positions(pos1 = c('C','W','D'), pos2 = 'G')
```

# Force Opposing Positions
When you want to ensure that two positions from opposite teams are included. For 
example, if you want to ensure that the lineups included at least one pair of 
Team A's QB and Team B's WR.

```{r}
opt <- opt %>%
  force_opposing_positions(pos1 = 'QB', pos2 = 'WR')
```

# Player Exposures

## Maximium Exposure
```{r}
# Set Carey Price's maximum exposure to .75
carey_price_id <- get_player_id(opt, name = 'Carey Price')
opt <- opt %>% 
  set_player_max_exp(carey_price_id, .75)
```

## Minimum Exposure
```{r}
# Set Nate Mackinnon's minimum exposure to .6
mackinnon_id <- get_player_id(opt, name = 'Nate MacKinnon')
opt <- opt %>% 
  set_player_min_exp(mackinnon_id, .6)
```

## Global Exposures 

Sometimes you want to set global exposures, so that no single player is selected
for a lineup more than X% of the time.  You can use the global maximum exposure for that.

**NOTE:** Individual player exposures supersede the global exposures. So, if you set
Sidney Crosby's Max-Exposure to .8, and the global max to .5, Sidney Crosby 
may end up in 80% of your lineups, while no other player will be greater than 50%.

The following sets the global max exposure to 50% -- so no single player will
be selected in more than 50% of lineups. (The actual percentage of lineups
can fluctuate slightly dependent on whether the total number of lineups 
you produce is evenly divisible by the percentage exposure)

```{r}
opt <- opt %>%
  set_max_exposure(.5)
```

# Specific Positions for FLEX/UTIL positions

This has no effect on lineups where no FLEX/UTIL positions are included.

```{r}

```

# Maximium Repeating Players

Set the maximum number of players allowed to repeat across lineups.

```{r}

```

# Set a minimum budget

```{r}

```

# Set Multiplier Position
This applies to Draftking's Captain Mode and Fanduel's MVP mode, where one player
is designated a multiplier position, where their salary and pts are doubled.

Sometimes, you may want to limit the set of players who are eligible for this
position (e.g., you definitely want either a QB or a WR, not DST or TE)

```{r}

```

# Variance

## Global Variance

## Player Level Variance

# Team Restrictions

## Set minimum number of teams to include

## Specify Players Per Team

### Max from teams

### Exact from teams